|

### 2020-02-02 analysis/paper/paper.Rmd
slight reorg or paragraph order

@@

These results are consistent with related findings for mark-resight studies where marked individuals are subject to incomplete identification. 
In such studies, accounting for failed identifications of marked individuals -- analogous to failed captures -- is most advantageous when identification probabilities are low -- analogous to capture probabilities being low [@mcclintock2014mark]. 
However, in the encounter-capture-recapture scenario considered here, we assume that whether an animal is marked or not is unknown until it is captured, as would be the case for subdermal passive integrated transponder tags in an amphibian [@gibbons2004pit].

@@

Looking ahead, there are opportunities to build upon this approach. 
First, in terms of implementation, marginalization over the discrete latent variables -- if possible -- could allow more efficient sampling from the posterior distribution. 
Second, because this model includes separate parameters for encounter and capture probabilities, covariates can be included separately for each of these components. 
This could be useful for example to account for predator avoidance behavior that might influence capture probabilities, and weather conditions that might influence encounter probabilities.
Observer effects provide an additional use case: some observers might be better than others at finding or capturing individual animals.

>>>>

These results are consistent with related findings for mark-resight studies where marked individuals are subject to incomplete identification. 
In such studies, accounting for failed identifications of marked individuals -- analogous to failed captures -- is most advantageous when identification probabilities are low -- analogous to capture probabilities being low [@mcclintock2014mark]. 
However, in the encounter-capture-recapture scenario considered here, whether an animal is marked or not is unknown until it is captured, as would be the case for subdermal passive integrated transponder tags in an amphibian [@gibbons2004pit].

@@

@@

Looking ahead, there are opportunities to build upon this approach. 
First, in terms of implementation, marginalization over the discrete latent variables might allow more efficient sampling from the posterior distribution. 
Second, because this model includes separate parameters for encounter and capture probabilities, covariates can be included separately for each of these components. 
This could be useful for example to account for predator avoidance behavior that might influence capture probabilities, and weather conditions that might influence encounter probabilities.
Observer effects provide an additional use case: some observers might be better than others at finding or capturing individual animals.
